---
title: "Gallery"
description: |
  Clicking on a thumbnail opens a viewer with viewing options and links to the code used to create the chart and the article or project that it's associated with.
output: 
  distill::distill_article:
    css: assets/css/gallery.css
base_url: https://ericbook.netlify.app/
---



```{r echo = FALSE}
knitr::opts_chunk$set(
  echo = FALSE
)

library(htmltools)
sub_html_ls <- readr::read_rds("data/sub-html-ls.rds")

```

<!-- css sheets go into head ---->
<head>

<!--- main lightgallery ---->
<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/css/lightgallery.min.css" integrity="sha512-DY7doCjzDiHKPjOIz7TBml+ZGeiORmxLdMEa8x7j+I0kuHD/vBogtvqhZCUbeCKJ8TR1slujyv9wxO4x0hbBMQ==" crossorigin="anonymous" referrerpolicy="no-referrer" />

<!-- lightgallery plugins -->

<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/css/lg-thumbnail.min.css" integrity="sha512-wHHBD+hSImJWcX192FT77uzFT4pVJDZ5sTiVYE3cArMtIix9lycXS0lvuLwRVyyFQO4pTj7MKxSuFKFMVzjK2w==" crossorigin="anonymous" referrerpolicy="no-referrer" />

<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/css/lg-share.min.css" integrity="sha512-dOqsuo1HGMv5ohBl/0OIUVzkwFLF8ZmjhpZp2VT2mpH5UuOJXwtBhxxtbrrEIpvTDWm7mESg0JsEl4zkUGv/gw==" crossorigin="anonymous" referrerpolicy="no-referrer" />

<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/css/lg-zoom.min.css" integrity="sha512-SGo05yQXwPFKXE+GtWCn7J4OZQBaQIakZSxQSqUyVWqO0TAv3gaF/Vox1FmG4IyXJWDwu/lXzXqPOnfX1va0+A==" crossorigin="anonymous" referrerpolicy="no-referrer" />

</head>


<!---- js scripts go into body ---->

<!--- main lightgallery ---->
<script src="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/lightgallery.min.js" integrity="sha512-BQPHJVHCOVIdd6S0Vi8+7gaPHy0cZxXNEzqn1gQWeYEMQMQDolld6PGJtShlVcCHEOwve3XHBwKaarmRO/Dnjw==" crossorigin="anonymous" referrerpolicy="no-referrer"></script>

<!-- lightgallery plugins -->
<script src="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/plugins/thumbnail/lg-thumbnail.min.js" integrity="sha512-k8FNBu1DIf1nYGu45clIvqvk93ViLsqArYSULTd1PDXGwH6uniTxMa+h7Ag669l/g/FzSOG2foKygGYD/MkAMA==" crossorigin="anonymous" referrerpolicy="no-referrer"></script>

<script src="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/plugins/share/lg-share.min.js" integrity="sha512-dzIgaUGIQD5lMqBh2gls2ERU0ReZqyBIOmJNOLm1NjhDzotZcRjZ1oja993dSRv62/dakvNsvwtXNOreTkAJ5A==" crossorigin="anonymous" referrerpolicy="no-referrer"></script>

<script src="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/plugins/zoom/lg-zoom.min.js" integrity="sha512-wPh5IuI7eIXXS7SXTd0Xou0c1abJIocKCfrbHUFwem9wnd/v0ALKl+S69DvLcUgOVDYqjmIl1HkCOJl9y0IDaQ==" crossorigin="anonymous" referrerpolicy="no-referrer"></script>




```{r create_layout}

# get image paths and create html scaffolding
# if using caption animation, recommend scaling gallery images to height = 645px

images <- tibble::tibble(
  # gallery doesn't work with full paths, so need to do some chopping and adding back-on
  images_thumb = basename(fs::dir_ls(here::here("images/gallery/thumbnails"))),
  images_full_size = basename(fs::dir_ls(here::here("images/gallery/large")))
  )

img_dims <- c("429-645-686", "912-645-1459", "766-645-1225", "1148-645-1836", "652-645-1043", "1180-645-1888", "1064-645-1702")

lol <- list(img_dims, images$images_full_size, sub_html_ls, images$images_thumb)

# lightgallery html skeleton
img_html <- tagList(purrr::pmap(lol, function(dim, l, s, t) {
  tags$a(
    "data-lg-size" = dim,
    "data-sizes" = "(min-width: 40em) 80vw, 100vw",
    class = "gallery-item",
    "data-src" = paste0("images/gallery/large/", l),
    "data-sub-html" = s,
    tags$img(src = paste0("images/gallery/thumbnails/", t),
             class = "img-fluid")
  )
}))

withTags(
  div(
    class = "gallery-container d-flex align-items-center justify-content-center",
    id = "gallery-container",
    img_html
  )
)

```


<!-- hideBarsDelay: 1500, Delay for hiding gallery controls in ms. ---->
<!-- speed: 500, chart transition speed in viewer in ms ---->
<!-- actualSize: true, lgZoom button to return chart to orig size ---->
<!-- showZoomInOutIcons: false, lgZoom ---->

<script type="text/javascript">
    // adds color to viewer background for each chart
    const colours = ['#304340', '#000', '#000', '#000', '#000', '#000', '#570101'];
    const galleryEventsBkgd = document.getElementById("gallery-container");
    galleryEventsBkgd.addEventListener('lgBeforeSlide', (event) => {
      const { index } = event.detail;
      document.querySelector('.lg-backdrop').style.backgroundColor =
        colours[index];
    });
    lightGallery(galleryEventsBkgd, {
      // Append caption inside the slide item
      // to apply some animation for the captions
      appendSubHtmlTo: ".lg-item",
      // Delay slide transition to complete captions animations
      // before navigating to different slides
      slideDelay: 400,
      speed: 500,
      showZoomInOutIcons: true,
      enableZoomAfter: 1000,
      scale: 0.5,
      plugins: [lgThumbnail, lgShare, lgZoom]
    });
</script>