---
title: "Gallery"
description: |
  Clicking on a thumbnail opens a viewer with viewing options and links to the code used to create the chart and the article or project that it's associated with.
output:
  distill::distill_article
base_url: https://ericbook.netlify.app/
---



```{r echo = FALSE}
knitr::opts_chunk$set(
  echo = FALSE
)

library(htmltools)
sub_html_ls <- readr::read_rds("data/sub-html-ls.rds")

```

<!-- css sheets go into head ---->
<head>

<!--- main lightgallery ---->
<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/css/lightgallery.min.css" integrity="sha512-DY7doCjzDiHKPjOIz7TBml+ZGeiORmxLdMEa8x7j+I0kuHD/vBogtvqhZCUbeCKJ8TR1slujyv9wxO4x0hbBMQ==" crossorigin="anonymous" referrerpolicy="no-referrer" />

<!-- lightgallery plugins -->

<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/css/lg-thumbnail.min.css" integrity="sha512-wHHBD+hSImJWcX192FT77uzFT4pVJDZ5sTiVYE3cArMtIix9lycXS0lvuLwRVyyFQO4pTj7MKxSuFKFMVzjK2w==" crossorigin="anonymous" referrerpolicy="no-referrer" />

<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/css/lg-share.min.css" integrity="sha512-dOqsuo1HGMv5ohBl/0OIUVzkwFLF8ZmjhpZp2VT2mpH5UuOJXwtBhxxtbrrEIpvTDWm7mESg0JsEl4zkUGv/gw==" crossorigin="anonymous" referrerpolicy="no-referrer" />

<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/css/lg-zoom.min.css" integrity="sha512-SGo05yQXwPFKXE+GtWCn7J4OZQBaQIakZSxQSqUyVWqO0TAv3gaF/Vox1FmG4IyXJWDwu/lXzXqPOnfX1va0+A==" crossorigin="anonymous" referrerpolicy="no-referrer" />

</head>


<!---- js scripts go into body ---->

<!--- main lightgallery ---->
<script src="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/lightgallery.min.js" integrity="sha512-BQPHJVHCOVIdd6S0Vi8+7gaPHy0cZxXNEzqn1gQWeYEMQMQDolld6PGJtShlVcCHEOwve3XHBwKaarmRO/Dnjw==" crossorigin="anonymous" referrerpolicy="no-referrer"></script>

<!-- lightgallery plugins -->
<script src="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/plugins/thumbnail/lg-thumbnail.min.js" integrity="sha512-k8FNBu1DIf1nYGu45clIvqvk93ViLsqArYSULTd1PDXGwH6uniTxMa+h7Ag669l/g/FzSOG2foKygGYD/MkAMA==" crossorigin="anonymous" referrerpolicy="no-referrer"></script>

<script src="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/plugins/share/lg-share.min.js" integrity="sha512-dzIgaUGIQD5lMqBh2gls2ERU0ReZqyBIOmJNOLm1NjhDzotZcRjZ1oja993dSRv62/dakvNsvwtXNOreTkAJ5A==" crossorigin="anonymous" referrerpolicy="no-referrer"></script>

<script src="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/2.1.8/plugins/zoom/lg-zoom.min.js" integrity="sha512-wPh5IuI7eIXXS7SXTd0Xou0c1abJIocKCfrbHUFwem9wnd/v0ALKl+S69DvLcUgOVDYqjmIl1HkCOJl9y0IDaQ==" crossorigin="anonymous" referrerpolicy="no-referrer"></script>


```{css}


.lightGallery-captions {
  h4 {
    transform: translate3d(60px, 0, 0px);
  }
  p {
    transform: translate3d(-60px, 0, 0px);
  }
  h4,
  p {
    opacity: 0;
  }
}
.lg-current {
  .lightGallery-captions {
    h4,
    p {
      transform: translate3d(0, 0, 0px);
    }
    h4,
    p {
      opacity: 1;
    }
  }
}
.lg-slide-progress {
  .lightGallery-captions {
    h4 {
      transform: translate3d(-60px, 0, 0px);
    }
    p {
      transform: translate3d(60px, 0, 0px);
    }
    h4,
    p {
      opacity: 0;
    }
  }
}

.lightGallery-captions {
  h4,
  p {
    transition: transform 0.4s ease-in-out, opacity 0.4s ease-in;
  }
}
.lg-current {
  .lightGallery-captions {
    h4,
    p {
      transition-delay: 500ms;
    }
  }
  &.lg-slide-progress {
    .lightGallery-captions {
      h4,
      p {
        transition-delay: 0ms;
      }
    }
  }
}



.gallery-item {
  width: 200px;
  padding: 5px;
}


```



```{r create_layout}

# get image paths and create html scaffolding

images <- tibble::tibble(
  # gallery doesn't work with full paths, so need to do some chopping and adding back-on
  images_thumb = basename(fs::dir_ls(here::here("images/gallery/thumbnails"))),
  images_full_size = basename(fs::dir_ls(here::here("images/gallery/large")))
  )


lol <- list(images$images_full_size, sub_html_ls, images$images_thumb)

# lightgallery html skeleton
img_html <- tagList(purrr::pmap(lol, function(l, s, t) {
  tags$a(
    class = "gallery-item",
    "data-src" = paste0("images/gallery/large/", l),
    "data-sub-html" = s,
    tags$img(src = paste0("images/gallery/thumbnails/", t),
             class = "img-fluid")
  )
}))

withTags(
  div(
    class = "gallery-container d-flex align-items-center justify-content-center",
    id = "gallery-container",
    img_html
  )
)

```


<!-- hideBarsDelay: 1500, Delay for hiding gallery controls in ms. ---->
<!-- speed: 400, chart transition speed in viewer in ms ---->
<!-- actualSize: lgzoom - true, button to return chart to orig size ---->
<!-- showZoomInOutIcons: lgzoom - false, literal ---->

<script type="text/javascript">
    lightGallery(document.getElementById("gallery-container"), {
      speed: 500,
      // Append caption inside the slide item
      // to apply some animation for the captions (Optional)
      appendSubHtmlTo: ".lg-item",
      // Delay slide transition to complete captions animations
      // before navigating to different slides (Optional)
      // You can find caption animation demo on the captions demo page
      slideDelay: 400,
      plugins: [lgZoom]
    });
</script>